---
title: "EDS241: Assignment 2"
author: "Allie Cole"
date: '`r format(Sys.time(), "%m/%d/%Y")`'
output: 
  pdf_document:
    toc: false
    number_sections: yes
header-includes:
  - \setlength{\parindent}{1em}
  - \usepackage{float}
--- 
  
``` {r setup, echo = FALSE, message = FALSE, warning = FALSE}

# set default chunk options
knitr::opts_chunk$set(fig.width = 4, fig.height = 3, 
                      echo = TRUE, message = FALSE, warning = FALSE)


# load packages
packages=c("stargazer", "here", "tidyr", "dplyr","stringr", "janitor", 
           "cowplot", "ggplot2", "tinytex", "datasets", "tibble", "kableExtra", "estimatr", "car", "broom")

for (i in packages) {
  if (require(i,character.only=TRUE)==FALSE) {
    install.packages(i,repos='http://cran.us.r-project.org')
  }
  else {
    require(i,character.only=TRUE)
  }
}

#devtools::install_github('rstudio/rmarkdown')
options(scipen=7) # not scientific notation


```


# Clean and plot data

\noindent The following code loads and cleans the data.

```{r , include=TRUE}

# Load data

library(readxl)
data1 <- read_excel("NBP.xls", sheet = 1, na = "NA") %>% 
  clean_names() 

```

The data included in the file NBP.xls, which is available on Gauchospace, are: fips (fips code
identifying each county), NBP (indicator =1 if the county was regulated under the NOx Budget
Program), PctBlack (fraction of the county population that is African American), and
Dnox_masstons (change in annual NOx emissions from all power plants in a county between
2000 and 2008 (in tons)). Note that the NBP market was in effect in 212 of the 485 counties in
the sample from 2003 to 2008, so the 2008-2000 change give us a sense of the program’s
effect on emissions. If emissions of NOx from power plants declined in a county, then
Dnox_masstons should be negative.

# Homework Questions 

### (a) Make a histogram depicting the distribution of Dnox_masstons.

```{r}
ggplot(data = data1, aes(x = dnox_masstons)) +
  geom_histogram() +
  theme_cowplot(14) +
  labs(x = "Low Birth Weight Percentage", 
       y = "Count")
```

### (b) Create an indicator =1 if the county has PctBlack above the sample median, and =0
otherwise (in the rest of the assignment, I refer to this variable as ‘D’). What is the average of
PctBlack for counties above the median, i.e. counties for which D=1?


### (c) Estimate a regression of Dnox_masstons on NBP. Interpret the estimated intercept and the
coefficient on NBP.


### (d) Create an interaction between the variables NBP and D. Estimate a regression of
Dnox_masstons on NBP, D, and this interaction. Interpret each estimated regression coefficient,
including the intercept.


### (e) What is the predicted Dnox_masstons in a county that was not regulated under NBP and
where PctBlack is above the sample median (i.e., where D=1)? Report the 95% confidence
interval for this prediction. Make sure to use “heteroskedasticity-robust” standard errors.









